Supplemental Material for \\ Helixer: Cross-species Gene Annotation of Large Eucaryotic Genomes Using Deep Learning

### 2020-04-24 paper/supplements.tex
detailed results added

\newpage
\section{In-depth model performance}

\begin{table}[!h]
\renewcommand\thetable{S1}
\centering
\begin{tabular}{@{}lll@{}}
\hline
Class & Animal Value & Plant Value \\ [0.5ex]
\hline
Intergenic & 0.7 & 0.3 \\
UTR & 1.6 & 1.0 \\
CDS & 1.2 & 0.9 \\
Intron & 1.2 & 0.3 \\
\hline
\end{tabular}
\caption{}
\end{table}

\newpage
\section{Model Evaluation by Species}
The following tables and plots show the prediction performance of Hexlixer for each species we worked with. The plots display the Subgenic F1 as well as the difference to AUGUSTUS with respect to the phylogenetic placement by NCBI Taxonomy.

@@

>>>>

\newpage
\section{Model Evaluation by Species}
The following tables and plots show the prediction performance of Hexlixer for each species we worked with. An F1 score of zero can indicate that the reference did not include that class. The plots display the Subgenic F1 as well as the difference to AUGUSTUS with respect to the phylogenetic placement by the NCBI taxonomy database \citep{federhen2012ncbi}.

@@

Genome & Acc Overall & IG F1 & UTR F1 & CDS F1 & Intron F1 & Subgenic F1 & Genic F1 \\ [0.5ex]
acanthochromis\_polyacanthus & 0.9036 & 0.9323 & 0.6 & 0.8663 & 0.8764 & 0.8753 & 0.8547 \\
ailuropoda\_melanoleuca & 0.9343 & 0.9488 & 0 & 0.8757 & 0.9173 & 0.9153 & 0.913 \\
amphilophus\_citrinellus & 0.8894 & 0.8501 & 0.0004 & 0.8609 & 0.9189 & 0.9123 & 0.9039 \\
amphiprion\_ocellaris & 0.9001 & 0.9304 & 0.5473 & 0.8391 & 0.8763 & 0.8723 & 0.8472 \\
amphiprion\_percula & 0.8942 & 0.923 & 0.5586 & 0.8375 & 0.8781 & 0.874 & 0.851 \\
anabas\_testudineus & 0.9036 & 0.93 & 0.6076 & 0.8632 & 0.9037 & 0.8978 & 0.8709 \\
anas\_platyrhynchos\_platyrhynchos & 0.9218 & 0.9498 & 0.3189 & 0.8432 & 0.8579 & 0.857 & 0.8478 \\
anolis\_carolinensis & 0.9051 & 0.942 & 0.4548 & 0.7631 & 0.788 & 0.7867 & 0.7776 \\
anser\_brachyrhynchus & 0.9286 & 0.9533 & 0.3737 & 0.8571 & 0.8766 & 0.8754 & 0.8675 \\
aotus\_nancymaae & 0.944 & 0.9629 & 0.3618 & 0.8557 & 0.9012 & 0.8996 & 0.895 \\
apteryx\_haastii & 0.9025 & 0.9207 & 0.2082 & 0.8287 & 0.89 & 0.886 & 0.8793 \\
apteryx\_owenii & 0.9072 & 0.935 & 0.3271 & 0.8354 & 0.8641 & 0.8623 & 0.8534 \\
apteryx\_rowi & 0.9102 & 0.9366 & 0.3352 & 0.8395 & 0.8716 & 0.8696 & 0.8608 \\
astatotilapia\_calliptera & 0.8663 & 0.9014 & 0.5666 & 0.7731 & 0.8438 & 0.8352 & 0.8169 \\
astyanax\_mexicanus & 0.8849 & 0.9124 & 0.5784 & 0.8246 & 0.8632 & 0.8601 & 0.8454 \\
betta\_splendens & 0.8423 & 0.8834 & 0.3626 & 0.8065 & 0.8227 & 0.8197 & 0.7842 \\
bison\_bison\_bison & 0.9021 & 0.9187 & 0 & 0.8575 & 0.8829 & 0.8819 & 0.8796 \\
bos\_indicus\_hybrid & 0.9304 & 0.9569 & 0.5481 & 0.8079 & 0.8505 & 0.8489 & 0.8414 \\
bos\_mutus & 0.9234 & 0.9498 & 0.3885 & 0.843 & 0.8593 & 0.8586 & 0.8525 \\
bos\_taurus & 0.9385 & 0.9622 & 0.4702 & 0.8379 & 0.8637 & 0.8627 & 0.8549 \\
caenorhabditis\_elegans & 0.7423 & 0.8288 & 0.1477 & 0.7385 & 0.5006 & 0.5965 & 0.5709 \\
calidris\_pugnax & 0.9166 & 0.9452 & 0.4135 & 0.8282 & 0.8568 & 0.8552 & 0.846 \\
calidris\_pygmaea & 0.9195 & 0.9461 & 0.4404 & 0.8485 & 0.8682 & 0.867 & 0.8576 \\
callithrix\_jacchus & 0.9352 & 0.9584 & 0.2818 & 0.833 & 0.8692 & 0.8679 & 0.8642 \\
callorhinchus\_milii & 0.8735 & 0.9123 & 0.3684 & 0.8019 & 0.8083 & 0.8079 & 0.7951 \\
canis\_familiaris & 0.9271 & 0.9542 & 0.2754 & 0.8239 & 0.8481 & 0.8472 & 0.8388 \\
canis\_lupus\_dingo & 0.937 & 0.9572 & 0.3463 & 0.8522 & 0.8976 & 0.8956 & 0.8906 \\
capra\_hircus & 0.9395 & 0.962 & 0.4262 & 0.8521 & 0.8767 & 0.8757 & 0.8695 \\
carlito\_syrichta & 0.9312 & 0.9554 & 0.4552 & 0.8477 & 0.8651 & 0.8644 & 0.8603 \\
castor\_canadensis & 0.9177 & 0.9467 & 0.3725 & 0.8477 & 0.843 & 0.8433 & 0.8356 \\
cavia\_aperea & 0.9405 & 0.9619 & 0 & 0.8462 & 0.8822 & 0.8805 & 0.8784 \\
cavia\_porcellus & 0.9462 & 0.968 & 0.5285 & 0.8483 & 0.8652 & 0.8645 & 0.8563 \\
cebus\_capucinus & 0.946 & 0.9659 & 0.5059 & 0.8455 & 0.8928 & 0.8911 & 0.885 \\
cercocebus\_atys & 0.9457 & 0.9658 & 0.4896 & 0.8506 & 0.8917 & 0.8902 & 0.8834 \\
chelonoidis\_abingdonii & 0.8808 & 0.9174 & 0.296 & 0.7582 & 0.8106 & 0.808 & 0.803 \\
chinchilla\_lanigera & 0.9437 & 0.9664 & 0.507 & 0.8537 & 0.862 & 0.8617 & 0.8527 \\
chlorocebus\_sabaeus & 0.9418 & 0.9645 & 0.4666 & 0.8569 & 0.8646 & 0.8643 & 0.8574 \\
choloepus\_hoffmanni & 0.9036 & 0.9253 & 0 & 0.7481 & 0.8818 & 0.8744 & 0.8725 \\
chrysemys\_picta\_bellii & 0.8882 & 0.9294 & 0.3391 & 0.7153 & 0.7733 & 0.7706 & 0.7631 \\
ciona\_intestinalis & 0.7474 & 0.8196 & 0.1528 & 0.6708 & 0.6638 & 0.6655 & 0.6383 \\
ciona\_savignyi & 0.7662 & 0.826 & 0.071 & 0.6471 & 0.6982 & 0.6878 & 0.6764 \\
clupea\_harengus & 0.863 & 0.9009 & 0.3972 & 0.7854 & 0.8341 & 0.8282 & 0.8018 \\
colobus\_angolensis\_palliatus & 0.9426 & 0.9631 & 0.5241 & 0.8557 & 0.8874 & 0.8863 & 0.8821 \\
cottoperca\_gobio & 0.8889 & 0.9177 & 0.5953 & 0.8284 & 0.8756 & 0.8694 & 0.848 \\
coturnix\_japonica & 0.9209 & 0.9461 & 0.3351 & 0.8604 & 0.8757 & 0.8747 & 0.8666 \\
cricetulus\_griseus\_picr & 0.9315 & 0.9546 & 0.3524 & 0.8647 & 0.8778 & 0.8772 & 0.8712 \\
crocodylus\_porosus & 0.917 & 0.9472 & 0.3471 & 0.8005 & 0.8337 & 0.8323 & 0.8262 \\
cyanistes\_caeruleus & 0.9228 & 0.9518 & 0.3437 & 0.8501 & 0.8445 & 0.8449 & 0.8362 \\
cynoglossus\_semilaevis & 0.8751 & 0.9027 & 0.5883 & 0.8718 & 0.8702 & 0.8704 & 0.8456 \\
cyprinodon\_variegatus & 0.8978 & 0.9298 & 0.5196 & 0.8531 & 0.8577 & 0.8573 & 0.835 \\
danio\_rerio & 0.873 & 0.9151 & 0.3666 & 0.7688 & 0.7974 & 0.7954 & 0.7734 \\
dasypus\_novemcinctus & 0.9371 & 0.9628 & 0.4583 & 0.8148 & 0.8328 & 0.832 & 0.8245 \\
denticeps\_clupeoides & 0.8766 & 0.9144 & 0.3753 & 0.8112 & 0.8603 & 0.8528 & 0.814 \\
dipodomys\_ordii & 0.9385 & 0.9599 & 0.4335 & 0.8549 & 0.8877 & 0.8863 & 0.8798 \\
dromaius\_novaehollandiae & 0.9118 & 0.9414 & 0.41 & 0.8481 & 0.8486 & 0.8486 & 0.8395 \\
drosophila\_melanogaster & 0.8409 & 0.8902 & 0.4738 & 0.9278 & 0.6762 & 0.7623 & 0.7467 \\
echinops\_telfairi & 0.7972 & 0.8476 & 0 & 0.741 & 0.7035 & 0.7048 & 0.7033 \\
electrophorus\_electricus & 0.8849 & 0.9176 & 0.3795 & 0.837 & 0.882 & 0.8749 & 0.84 \\
eptatretus\_burgeri & 0.7511 & 0.8463 & 0.1436 & 0.5056 & 0.3671 & 0.371 & 0.3674 \\
equus\_asinus\_asinus & 0.9301 & 0.9476 & 0.2589 & 0.8651 & 0.9073 & 0.9055 & 0.9011 \\

\clearpage
Genome & Acc Overall & IG F1 & UTR F1 & CDS F1 & Intron F1 & Subgenic F1 & Genic F1 \\ [0.5ex]
equus\_caballus & 0.9327 & 0.9571 & 0.2984 & 0.8417 & 0.8686 & 0.8675 & 0.86 \\
erinaceus\_europaeus & 0.8202 & 0.863 & 0 & 0.7519 & 0.7471 & 0.7472 & 0.7454 \\
erpetoichthys\_calabaricus & 0.8659 & 0.9173 & 0.3119 & 0.6275 & 0.6816 & 0.6794 & 0.6738 \\
esox\_lucius & 0.8749 & 0.912 & 0.5692 & 0.8331 & 0.8293 & 0.8297 & 0.8123 \\
felis\_catus & 0.9301 & 0.9557 & 0.3452 & 0.85 & 0.8561 & 0.8559 & 0.8494 \\
ficedula\_albicollis & 0.9287 & 0.9559 & 0.5561 & 0.8493 & 0.8587 & 0.8581 & 0.8473 \\
fukomys\_damarensis & 0.9434 & 0.9664 & 0.4492 & 0.8454 & 0.857 & 0.8565 & 0.8479 \\
fundulus\_heteroclitus & 0.8951 & 0.927 & 0.543 & 0.8397 & 0.863 & 0.8609 & 0.84 \\
gadus\_morhua & 0.886 & 0.8931 & 0 & 0.8422 & 0.8924 & 0.887 & 0.8806 \\
gallus\_gallus & 0.9325 & 0.9575 & 0.4856 & 0.8165 & 0.8784 & 0.8743 & 0.8637 \\
gambusia\_affinis & 0.8873 & 0.9182 & 0.5344 & 0.8719 & 0.875 & 0.8747 & 0.8437 \\
gasterosteus\_aculeatus & 0.8774 & 0.8987 & 0.1991 & 0.8583 & 0.8969 & 0.8896 & 0.8568 \\
gopherus\_agassizii & 0.8679 & 0.9133 & 0.3725 & 0.7513 & 0.7523 & 0.7522 & 0.7456 \\
gorilla\_gorilla & 0.9422 & 0.9635 & 0.5272 & 0.8459 & 0.8808 & 0.8796 & 0.8748 \\
gouania\_willdenowi & 0.8533 & 0.8976 & 0.2835 & 0.7337 & 0.805 & 0.7979 & 0.7674 \\
haplochromis\_burtoni & 0.9008 & 0.9309 & 0.6155 & 0.8732 & 0.8684 & 0.8689 & 0.8492 \\
heterocephalus\_glaber\_female & 0.9416 & 0.9644 & 0.4958 & 0.828 & 0.8665 & 0.865 & 0.8565 \\
hippocampus\_comes & 0.8695 & 0.9026 & 0.4316 & 0.8332 & 0.8622 & 0.8581 & 0.83 \\
homo\_sapiens & 0.9492 & 0.9701 & 0.4823 & 0.8367 & 0.8648 & 0.8639 & 0.8553 \\
hucho\_hucho & 0.874 & 0.9203 & 0.3735 & 0.7266 & 0.7813 & 0.7754 & 0.7537 \\
ictalurus\_punctatus & 0.8791 & 0.9124 & 0.5555 & 0.8398 & 0.849 & 0.8481 & 0.8279 \\
ictidomys\_tridecemlineatus & 0.944 & 0.9655 & 0.5465 & 0.8627 & 0.8771 & 0.8765 & 0.8686 \\
jaculus\_jaculus & 0.9344 & 0.9578 & 0.2006 & 0.8484 & 0.8692 & 0.8685 & 0.8632 \\
junco\_hyemalis & 0.9308 & 0.9538 & 0.4298 & 0.8626 & 0.893 & 0.8911 & 0.8797 \\
kryptolebias\_marmoratus & 0.8961 & 0.9269 & 0.5683 & 0.8598 & 0.8748 & 0.873 & 0.8458 \\
labrus\_bergylta & 0.894 & 0.9237 & 0.5812 & 0.8426 & 0.8788 & 0.8741 & 0.8513 \\
larimichthys\_crocea & 0.8758 & 0.9079 & 0.3582 & 0.8572 & 0.8693 & 0.8677 & 0.8282 \\
lates\_calcarifer & 0.8741 & 0.9062 & 0.3905 & 0.8387 & 0.867 & 0.8632 & 0.8276 \\
latimeria\_chalumnae & 0.8817 & 0.9251 & 0.3917 & 0.7154 & 0.7628 & 0.7605 & 0.7529 \\
lepidothrix\_coronata & 0.9261 & 0.9489 & 0.4337 & 0.8596 & 0.8919 & 0.8899 & 0.8805 \\
lepisosteus\_oculatus & 0.9119 & 0.9401 & 0.5533 & 0.8676 & 0.8706 & 0.8703 & 0.8559 \\
lonchura\_striata\_domestica & 0.9261 & 0.9503 & 0.43 & 0.8522 & 0.8859 & 0.8837 & 0.8731 \\
loxodonta\_africana & 0.9311 & 0.948 & 0 & 0.8752 & 0.9058 & 0.9044 & 0.9024 \\
macaca\_fascicularis & 0.9452 & 0.9654 & 0.4878 & 0.8549 & 0.8897 & 0.8885 & 0.8821 \\
macaca\_mulatta & 0.9416 & 0.9637 & 0.3885 & 0.8124 & 0.876 & 0.8738 & 0.8664 \\
macaca\_nemestrina & 0.946 & 0.966 & 0.4801 & 0.8495 & 0.8916 & 0.8901 & 0.8833 \\
manacus\_vitellinus & 0.9125 & 0.9426 & 0.3877 & 0.8354 & 0.8483 & 0.8475 & 0.8378 \\
mandrillus\_leucophaeus & 0.9414 & 0.9623 & 0.5191 & 0.8525 & 0.8856 & 0.8844 & 0.8802 \\
marmota\_marmota\_marmota & 0.9238 & 0.9439 & 0.3195 & 0.8671 & 0.8922 & 0.8911 & 0.8869 \\
mastacembelus\_armatus & 0.8885 & 0.9193 & 0.6051 & 0.8577 & 0.8714 & 0.8695 & 0.8464 \\
maylandia\_zebra & 0.8784 & 0.9159 & 0.5813 & 0.762 & 0.8453 & 0.8352 & 0.8151 \\
meleagris\_gallopavo & 0.912 & 0.9324 & 0.3154 & 0.8695 & 0.8911 & 0.8895 & 0.8826 \\
melopsittacus\_undulatus & 0.9237 & 0.9493 & 0.4358 & 0.8516 & 0.8732 & 0.8719 & 0.8632 \\
meriones\_unguiculatus & 0.9295 & 0.9535 & 0.4615 & 0.8735 & 0.8772 & 0.877 & 0.8682 \\
mesocricetus\_auratus & 0.9448 & 0.9657 & 0.5247 & 0.8626 & 0.8837 & 0.8828 & 0.8759 \\
microcebus\_murinus & 0.9429 & 0.9645 & 0.494 & 0.8372 & 0.8818 & 0.8801 & 0.8724 \\
microtus\_ochrogaster & 0.9443 & 0.9646 & 0.5009 & 0.864 & 0.8923 & 0.8911 & 0.8831 \\
mola\_mola & 0.8815 & 0.653 & 0 & 0.8648 & 0.9275 & 0.9197 & 0.9095 \\
monodelphis\_domestica & 0.9257 & 0.9562 & 0.3206 & 0.7962 & 0.7846 & 0.785 & 0.7792 \\
monopterus\_albus & 0.8819 & 0.9102 & 0.5546 & 0.8518 & 0.8671 & 0.8653 & 0.8461 \\
mus\_caroli & 0.9372 & 0.9623 & 0.4256 & 0.8419 & 0.8348 & 0.8351 & 0.8305 \\
mus\_musculus & 0.9542 & 0.9736 & 0.6151 & 0.8638 & 0.8659 & 0.8658 & 0.8569 \\
mus\_pahari & 0.9352 & 0.9608 & 0.4229 & 0.8431 & 0.8344 & 0.8347 & 0.8301 \\
mus\_spicilegus & 0.9339 & 0.9583 & 0.4436 & 0.8647 & 0.863 & 0.8631 & 0.8562 \\
mus\_spretus & 0.9337 & 0.96 & 0.4093 & 0.8314 & 0.8267 & 0.8269 & 0.8224 \\
mustela\_putorius\_furo & 0.9317 & 0.9578 & 0.4319 & 0.857 & 0.8494 & 0.8497 & 0.8413 \\
myotis\_lucifugus & 0.942 & 0.9622 & 0.0703 & 0.8534 & 0.9013 & 0.8983 & 0.8933 \\
nannospalax\_galili & 0.9486 & 0.9685 & 0.4998 & 0.8469 & 0.8844 & 0.883 & 0.8767 \\
neolamprologus\_brichardi & 0.8895 & 0.9094 & 0.4797 & 0.8523 & 0.8911 & 0.8868 & 0.8696 \\
neovison\_vison & 0.9362 & 0.9565 & 0.4219 & 0.8752 & 0.895 & 0.8942 & 0.8894 \\

\clearpage
Genome & Acc Overall & IG F1 & UTR F1 & CDS F1 & Intron F1 & Subgenic F1 & Genic F1 \\ [0.5ex]
nomascus\_leucogenys & 0.9433 & 0.9634 & 0.489 & 0.8497 & 0.8912 & 0.8897 & 0.8856 \\
notamacropus\_eugenii & 0.8951 & 0.9203 & 0 & 0.7692 & 0.8619 & 0.8567 & 0.8552 \\
notechis\_scutatus & 0.8491 & 0.89 & 0.2625 & 0.7682 & 0.7845 & 0.7834 & 0.776 \\
nothoprocta\_perdicaria & 0.9062 & 0.8467 & 0 & 0.8533 & 0.9358 & 0.9294 & 0.9255 \\
numida\_meleagris & 0.9276 & 0.952 & 0.3472 & 0.8565 & 0.8803 & 0.8788 & 0.871 \\
ochotona\_princeps & 0.8374 & 0.8737 & 0 & 0.7899 & 0.7795 & 0.7799 & 0.7776 \\
octodon\_degus & 0.9381 & 0.9602 & 0.198 & 0.8305 & 0.8797 & 0.8778 & 0.8721 \\
oreochromis\_niloticus & 0.8967 & 0.9299 & 0.5269 & 0.8292 & 0.8495 & 0.8472 & 0.8284 \\
ornithorhynchus\_anatinus & 0.9007 & 0.939 & 0.4056 & 0.7987 & 0.7723 & 0.7738 & 0.7665 \\
oryctolagus\_cuniculus & 0.9025 & 0.9397 & 0.2709 & 0.7731 & 0.7786 & 0.7784 & 0.7715 \\
oryzias\_latipes & 0.8864 & 0.9179 & 0.6008 & 0.8146 & 0.8671 & 0.8609 & 0.8401 \\
oryzias\_melastigma & 0.8842 & 0.9189 & 0.5583 & 0.8437 & 0.8535 & 0.8524 & 0.8265 \\
otolemur\_garnettii & 0.95 & 0.9681 & 0.1822 & 0.8767 & 0.9011 & 0.9001 & 0.8954 \\
ovis\_aries & 0.9325 & 0.9569 & 0.2919 & 0.8441 & 0.8695 & 0.8684 & 0.8622 \\
pan\_paniscus & 0.9532 & 0.972 & 0.5101 & 0.8553 & 0.8818 & 0.8809 & 0.8757 \\
pan\_troglodytes & 0.9458 & 0.9665 & 0.499 & 0.8469 & 0.8822 & 0.881 & 0.8745 \\
panthera\_pardus & 0.9366 & 0.9592 & 0.498 & 0.8428 & 0.8787 & 0.8774 & 0.8716 \\
panthera\_tigris\_altaica & 0.9289 & 0.954 & 0.4484 & 0.835 & 0.8641 & 0.863 & 0.8574 \\
papio\_anubis & 0.943 & 0.9608 & 0.3066 & 0.8673 & 0.9071 & 0.9057 & 0.9019 \\
parambassis\_ranga & 0.8571 & 0.8962 & 0.3735 & 0.8001 & 0.845 & 0.8375 & 0.7963 \\
paramormyrops\_kingsleyae & 0.8926 & 0.925 & 0.591 & 0.8542 & 0.8639 & 0.8628 & 0.8418 \\
parus\_major & 0.9307 & 0.955 & 0.3955 & 0.8683 & 0.8818 & 0.881 & 0.8703 \\
pelodiscus\_sinensis & 0.8755 & 0.92 & 0.348 & 0.6937 & 0.7558 & 0.7529 & 0.744 \\
periophthalmus\_magnuspinnatus & 0.9109 & 0.9341 & 0 & 0.8391 & 0.9087 & 0.8999 & 0.889 \\
peromyscus\_maniculatus\_bairdii & 0.9164 & 0.9274 & 0.002 & 0.8843 & 0.9059 & 0.905 & 0.903 \\
petromyzon\_marinus & 0.9126 & 0.9496 & 0.094 & 0.714 & 0.8285 & 0.8155 & 0.8039 \\
phascolarctos\_cinereus & 0.9254 & 0.953 & 0.3568 & 0.8302 & 0.8395 & 0.8392 & 0.8336 \\
piliocolobus\_tephrosceles & 0.9374 & 0.9571 & 0.3872 & 0.8289 & 0.8967 & 0.8942 & 0.8908 \\
poecilia\_formosa & 0.8969 & 0.9291 & 0.5553 & 0.8592 & 0.8762 & 0.8742 & 0.8445 \\
poecilia\_latipinna & 0.8973 & 0.9281 & 0.4831 & 0.8562 & 0.879 & 0.8763 & 0.8486 \\
poecilia\_mexicana & 0.8975 & 0.9298 & 0.5679 & 0.8584 & 0.8696 & 0.8683 & 0.8422 \\
poecilia\_reticulata & 0.8654 & 0.8732 & 0.4516 & 0.8738 & 0.8772 & 0.8768 & 0.8591 \\
pogona\_vitticeps & 0.8852 & 0.9268 & 0.2963 & 0.7753 & 0.7736 & 0.7737 & 0.7641 \\
pongo\_abelii & 0.9393 & 0.9631 & 0.5004 & 0.8195 & 0.8536 & 0.8525 & 0.8472 \\
procavia\_capensis & 0.8892 & 0.9093 & 0 & 0.7863 & 0.8673 & 0.8636 & 0.8619 \\
prolemur\_simus & 0.9409 & 0.9534 & 0 & 0.885 & 0.9256 & 0.9239 & 0.9223 \\
propithecus\_coquereli & 0.9408 & 0.9613 & 0.4612 & 0.854 & 0.8906 & 0.8892 & 0.8844 \\
pteropus\_vampyrus & 0.8878 & 0.9056 & 0 & 0.8487 & 0.8679 & 0.8669 & 0.8647 \\
pundamilia\_nyererei & 0.9026 & 0.9284 & 0.5454 & 0.8598 & 0.8918 & 0.8882 & 0.868 \\
pygocentrus\_nattereri & 0.9061 & 0.9327 & 0.5784 & 0.8557 & 0.8799 & 0.878 & 0.8611 \\
rattus\_norvegicus & 0.9436 & 0.9674 & 0.4773 & 0.8384 & 0.8336 & 0.8338 & 0.8247 \\
rhinopithecus\_bieti & 0.9438 & 0.9645 & 0.4634 & 0.8464 & 0.8876 & 0.8861 & 0.8799 \\
rhinopithecus\_roxellana & 0.9446 & 0.9647 & 0.5251 & 0.8489 & 0.8918 & 0.8901 & 0.8843 \\
saimiri\_boliviensis\_boliviensis & 0.9412 & 0.9625 & 0.5019 & 0.8488 & 0.884 & 0.8828 & 0.8771 \\
salvator\_merianae & 0.8947 & 0.9334 & 0.3899 & 0.7896 & 0.782 & 0.7824 & 0.774 \\
sarcophilus\_harrisii & 0.9245 & 0.9523 & 0.4197 & 0.8504 & 0.8387 & 0.8392 & 0.8336 \\
scleropages\_formosus & 0.9055 & 0.9342 & 0.5883 & 0.8616 & 0.8885 & 0.8855 & 0.8633 \\
scophthalmus\_maximus & 0.8944 & 0.9223 & 0.6249 & 0.8864 & 0.8822 & 0.8828 & 0.8575 \\
serinus\_canaria & 0.9198 & 0.9463 & 0.4193 & 0.8563 & 0.8723 & 0.8713 & 0.8605 \\
seriola\_dumerili & 0.9002 & 0.9263 & 0.5769 & 0.8745 & 0.8923 & 0.8902 & 0.8646 \\
seriola\_lalandi\_dorsalis & 0.903 & 0.9289 & 0.6162 & 0.8732 & 0.8925 & 0.89 & 0.8679 \\
sorex\_araneus & 0.8512 & 0.8868 & 0 & 0.7659 & 0.7934 & 0.7923 & 0.7901 \\
spermophilus\_dauricus & 0.9238 & 0.9418 & 0 & 0.8297 & 0.9005 & 0.8974 & 0.8951 \\
sphenodon\_punctatus & 0.8151 & 0.884 & 0.2405 & 0.5038 & 0.5878 & 0.5838 & 0.58 \\
stegastes\_partitus & 0.9075 & 0.9332 & 0.577 & 0.8697 & 0.8949 & 0.8922 & 0.87 \\
sus\_scrofa & 0.9186 & 0.952 & 0.4099 & 0.731 & 0.8049 & 0.8018 & 0.7894 \\
taeniopygia\_guttata & 0.8963 & 0.8963 & 0.2082 & 0.8642 & 0.9045 & 0.9017 & 0.8963 \\
takifugu\_rubripes & 0.8759 & 0.9133 & 0.5619 & 0.8475 & 0.86 & 0.8575 & 0.8282 \\
tetraodon\_nigroviridis & 0.8745 & 0.8944 & 0.1826 & 0.8695 & 0.8888 & 0.8838 & 0.8602 \\
theropithecus\_gelada & 0.9554 & 0.9694 & 0.5335 & 0.8786 & 0.9283 & 0.9266 & 0.9233 \\

\clearpage
\begin{table}[!h]
\resizebox{\textwidth}{!}{%
\renewcommand\thetable{S1}
\centering
\begin{tabular}{@{}llllllll@{}}
\hline
Genome & Acc Overall & IG F1 & UTR F1 & CDS F1 & Intron F1 & Subgenic F1 & Genic F1 \\ [0.5ex]
\hline
tupaia\_belangeri & 0.8092 & 0.8584 & 0 & 0.732 & 0.7162 & 0.7167 & 0.7147 \\
tursiops\_truncatus & 0.8792 & 0.8984 & 0 & 0.8473 & 0.8556 & 0.8552 & 0.8535 \\
urocitellus\_parryii & 0.9391 & 0.9593 & 0.4454 & 0.8788 & 0.8948 & 0.8941 & 0.888 \\
ursus\_americanus & 0.9168 & 0.9455 & 0.3849 & 0.8449 & 0.8512 & 0.8508 & 0.8433 \\
ursus\_maritimus & 0.9257 & 0.9528 & 0.3279 & 0.8313 & 0.8528 & 0.852 & 0.8453 \\
vicugna\_pacos & 0.8516 & 0.886 & 0 & 0.7738 & 0.7945 & 0.7939 & 0.7923 \\
vombatus\_ursinus & 0.9315 & 0.9572 & 0.4186 & 0.8413 & 0.8494 & 0.8491 & 0.8425 \\
vulpes\_vulpes & 0.9349 & 0.9595 & 0.3522 & 0.8444 & 0.8616 & 0.8609 & 0.8541 \\
xenopus\_tropicalis & 0.8699 & 0.9175 & 0.317 & 0.7277 & 0.7438 & 0.7427 & 0.7289 \\
xiphophorus\_couchianus & 0.8575 & 0.5599 & 0 & 0.8585 & 0.9119 & 0.9052 & 0.8932 \\
xiphophorus\_maculatus & 0.8854 & 0.9156 & 0.5964 & 0.8368 & 0.871 & 0.8671 & 0.8439 \\
zonotrichia\_albicollis & 0.9216 & 0.9482 & 0.382 & 0.8601 & 0.8667 & 0.8663 & 0.857 \\
\hline
\end{tabular}}
\end{table}
